Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/sw-contract.tex

The assumption on \lineref{line:sw-assume-3} constrains when a request can arrive by reasoning about the \emph{state} of the contract defined be the associated streams.
When writing assumptions and guarantees, it is important to differentiate pre-state, before a contract updates its state, and post-state, after a contract updates its state, in response to the current input.
The \texttt{pre} naturally makes that distinction.
In general, assumptions regarding state should be evaluated in the pre-state of the component with the current inputs, and guarantees regarding state should be evaluated on the post-state of the component given the current inputs.
Additionally, guarantees should use \texttt{pre} anytime they need to reason about the current state relative to the previous state.

>>>>

The assumption on \lineref{line:sw-assume-3} constrains when a request
can arrive by reasoning about the \emph{state} of the contract defined
by the associated streams.  When writing assumptions and guarantees,
it is important to differentiate pre-state, before a contract updates
its state, and post-state, after a contract updates its state, in
response to the current input.  The \texttt{pre} naturally makes that
distinction.  In general, assumptions regarding state should be
evaluated in the pre-state of the component with the current inputs,
and guarantees regarding state should be evaluated on the post-state
of the component given the current inputs.  Additionally, guarantees
should use \texttt{pre} anytime they need to reason about the current
state relative to the previous state.
